Joint analysis of read count data

### 2020-09-04 combined_analysis/combine_all_data.Rmd
Fix Dx

@@

@@

>>>>

METADATA$Dx = factor(METADATA$Dx, c('Control', 'BP', "SCZ"))

@@

names(Lbase)

# SCZ by sex
L_SCZ = Lbase
L_SCZ['DxSCZ:Reported_GenderMale'] = 1
L_SCZ['Reported_GenderMale'] = -1
L_SCZ['DxSCZ'] = -1
L_SCZ['DxControl'] = 1 
# (A - B) - (C - D) = A - B - C + D

# BP by sex
L_BP = Lbase
L_SCZ['DxBP:Reported_GenderMale'] = 1
L_SCZ['Reported_GenderMale'] = -1
L_SCZ['DxBP'] = -1
L_SCZ['DxControl'] = 1

L = cbind(	SczSex = L_SCZ,
			BPSex = L_BP)

@@

```{r plots.interaction.DxSex, fig.width=10, fig.height=5}
# Disease
tab = topTable(fit_marginal, "SczSex", number=Inf) %>% getGeneSymbol
fig1 = plotVolcano( tab, tab$Symbol[1:20] ) + ggtitle("SCZ")

tab = topTable(fit_marginal, "BPSex", number=Inf)  %>% getGeneSymbol
fig2 = plotVolcano( tab, tab$Symbol[1:20] ) + ggtitle("BP")

plot_grid( fig1, fig2, ncol=2) 
```
